%-----------------------------------------------------------------------------------------------%
%
% % Oktober 2022
% Template Latex untuk Laporan Kerja Praktek Program Studi Sistem informasi ini
% Dikembangkan oleh Daffa Takratama Savra (daffatakratama13@gmail.com)

% Template ini dikembangkan dari template yang dibuat oleh Inggih Permana (inggihjava@gmail.com).

% Orang yang cerdas adalah orang yang paling banyak mengingat kematian.
%
%-----------------------------------------------------------------------------------------------%
\fontsize{12}{14.4}
\begin{center}\MakeUppercase{\textbf{\emph{Abstract}}}\end{center}

\noindent
\fontsize{10pt}{12pt}\selectfont
\emph{The Information Systems Study Program at the Faculty of Science and Technology of UIN Suska Riau has long been a center of focus in the field of Information Technology. However, inventory management in laboratories such as Information Systems Engineering, Internet, and Software Engineering Laboratories is still done manually, resulting in inefficiency in inventory data management. To solve this problem, SITARIS, an inventory information system, was implemented using the CodeIgniter 4 framework. CodeIgniter's advantages in size and efficiency made it the main choice. This research aims to implement an effective and efficient computerized inventory information system in the Information Systems Laboratory. Through the application of the CodeIgniter 4 framework, the management of goods in the laboratory can be facilitated. The benefits include data processing efficiency, better inventory management, quick access to inventory information, documentation, loan management, as well as better decision-making in maintenance and funding allocation. Thus, the development of SITARIS with the CodeIgniter 4 framework will provide significant benefits to the Information Systems Laboratory.}\\
\noindent{\emph{\textbf{Keywords:} \textit{CodeIgniter, Information System, Laboratory Inventory, MariaDB, PHP}}} \\